AmphibBio

### 2020-06-19 data-raw/amphibio.Rmd
update helper functions and fix amphbio processing

amph <- read_csv(system.file("extdata", "amphibio/AmphiBIO_v1.csv", package = "biodivTS"))

amphibio <- amph %>%
  mutate(id = get_ids(Species, "itis")) %>%
  filter(!is.na(id)) %>%
  mutate(scientificName = get_names(id, "itis")) %>%
  select(id, scientificName, Species) %>%
  right_join(select(amph, -id), by = "Species") %>%
  rename(sourceName = Species) %>%
  select(-c("Order", "Family", "Genus"))

# Using by_ doesn't give any additional ids
# amphibio <- by_name(amph$Species, "itis") %>%
#   filter(taxonRank == "species") %>% #only want ID's to species, since that's the level of the trait data
#   drop_na(acceptedNameUsageID)
```

@@

add_syn_res <- syn_res %>% 
  filter(!input %in% alt_dupes$input) %>% #excluding duplicate matched species
  select(id = acceptedNameUsageID, sourceName = input, scientificName) %>%
  distinct() %>%
  group_by(sourceName) %>%
  top_n(1, scientificName) %>%
  left_join(amphibio %>% select(-c(id, scientificName)), by = "sourceName", na_matches =  "never") %>%
  ungroup() %>%
  distinct()

>>>>

amph <- read_csv(system.file("extdata", "amphibio/AmphiBIO_v1.csv", package = "biodivTS")) %>%
  select(-id) %>%
  rename_all(tolower) %>%
  rename(diet_leaves = leaves, diet_flowers = flowers, diet_seed = seeds, diet_fruit = fruits, diet_inv = arthro, diet_vert = vert,
         diurnal = diu, nocturnal = noc, crepuscular = crepu, bodymass_value = body_mass_g) %>%
  mutate(diet_seed = as.numeric(diet_seed))

amphibio <- amph %>%
  mutate(id = get_ids(species, "itis")) %>%
  filter(!is.na(id)) %>%
  mutate(scientificName = get_names(id, "itis")) %>%
  select(id, scientificName, species) %>%
  right_join(amph, by = "species") %>%
  rename(sourceName = species) %>%
  select(-c("order", "family", "genus"))

#two entries need to be resolved by hand
add_ids <- amphibio %>%
  filter(is.na(id)) %>%
  pull(sourceName) %>%
  filter_name(., "itis") %>%
  filter(!is.na(acceptedNameUsageID)) %>%
  select(scientificName, id = acceptedNameUsageID) %>%
  distinct() %>%
  left_join(amph, by = c("scientificName" = "species")) %>%
  select(-c("order", "family", "genus")) %>%
  mutate(sourceName = scientificName)

amphibio <- amphibio %>% 
  filter(!sourceName %in% add_ids$sourceName) %>%
  bind_rows(add_ids)
```

@@

add_syn_res <- syn_res %>% 
  filter(!input %in% alt_dupes$input) %>% #excluding duplicate matched species
  select(id = acceptedNameUsageID, sourceName = input) %>%
  distinct() %>%
  mutate(scientificName = get_names(id, "itis")) %>%
  left_join(amphibio %>% select(-c(id, scientificName)), by = "sourceName", na_matches =  "never") %>%
  distinct()
